Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-08 docs/lo_density/lo_density.tex
finished with my comments for how I think we can make the cutoff treatment consistent.  These are subtle details which shouldn't "fix" test_basestate.

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0^{\rm cart} > {\tt base\_cutoff\_density}$ 
  (in spherical).
  \MarginPar{Spherical should cue off the coordinate.}

@@

\item In {\tt update\_scal}, if $\rho < {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.
  \MarginPar{Perhaps $\rho \le {\tt base\_cutoff\_density}$}

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.
  \MarginPar{Cue off the coordinate?}

>>>>

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0^{\rm cart} > {\tt base\_cutoff\_density}$ 
  (in spherical).
  \MarginPar{For plane-parallel, I think we should use 
    $r \le {\tt base\_cutoff\_density\_coord}$.}

@@

\item In {\tt update\_scal}, if $\rho < {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.
  \MarginPar{I think we want $\rho \le {\tt base\_cutoff\_density}$}

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.
  \MarginPar{I think this needs to be reworked to include mass up to the 
    cell-centered location of {\tt base\_cutoff\_density\_coord} for both cell 
    and edge gravity.}
